Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-13 emsoft-2019/related.tex
updates

% control-only
\paragraph{Controller Synthesis}
The problem of controller synthesis under safety requirements on the states has
been investigated mostly for Model Predictive Control (MPC)~\cite{camacho2013model} (also called receding horizon control).
Researchers have investigated designing MPC controllers for satisfying safety requirements expressed as temporal logic formulas 
\cite{FMPS18,KaramanSF08,raman2014model,WongpiromsarnTM12,pant2017smooth,kim2017dynamic}.
%,LiNSXL17, SadighK16,
%\Sadegh{We can reduce the references.}
The main technique is to optimize the robust satisfaction of 
the formula~\cite{donze2010robust} (i.e., a quantitative measure of satisfaction).
These works utilize MPC an an online method that requires solving at runtime often computationally 
expensive optimization problems. In contrast, the explicit MPC used in our work performs controller synthesis at the design time.

@@

% finite-precision only
\paragraph{Finite-Precision Optimization}
General-purpose techniques for synthesizing fixed-point implementations of 
arithmetic expressions have been developed in the space of embedded systems,
where resource efficiency is generally important.
Some work has used dynamic analyses for estimating
errors~\cite{Gaffar2004,Mallik2007}, which, however, do not provide guarantees.
Several approaches~\cite{Lee2006,Osborne2007,Kinsman2009,Pang2011} use sound
error analysis techniques and perform mixed-precision optimization~\cite{Lee2006,Pang2011},
similar to the approach implemented in the tool Daisy used in this paper.
An alternate way to bound errors in fixed point implementations of EMPC 
through mixed integer programming is given by~\citet{imperialrmpc}.

>>>>

% control-only
\paragraph{Controller Synthesis}
The problem of controller synthesis under safety requirements on the states has
been investigated mostly for Model Predictive Control (MPC)~\cite{camacho2013model} (also called receding horizon control).
Researchers have investigated designing MPC controllers for satisfying safety requirements expressed as temporal logic formulas 
\cite{FMPS18,KaramanSF08,raman2014model,WongpiromsarnTM12,pant2017smooth,kim2017dynamic}.
%,LiNSXL17, SadighK16,
%\Sadegh{We can reduce the references.}
The main technique is to optimize the robust satisfaction of 
the formula~\cite{donze2010robust} (i.e., a quantitative measure of satisfaction).
These works utilize MPC an an online method that requires solving at runtime often computationally 
expensive optimization problems. In contrast, the explicit MPC used in our work performs controller synthesis at the design time.
Synthesizing digital controllers with formal guarantees while having finite-precision implementation is studied in \cite{SSPBLSZ19} for stochastic systems.

@@

% finite-precision only
\paragraph{Finite-Precision Optimization}
General-purpose techniques for synthesizing fixed-point implementations of 
arithmetic expressions have been developed in the space of embedded systems,
where resource efficiency is generally important.
Some work has used dynamic analyses for estimating
errors~\cite{Gaffar2004,Mallik2007}, which, however, do not provide guarantees.
Several approaches~\cite{Lee2006,Osborne2007,Kinsman2009,Pang2011} use sound
error analysis techniques and perform mixed-precision optimization~\cite{Lee2006,Pang2011},
similar to the approach implemented in the tool Daisy used in this paper.
An alternative way of bounding errors in fixed-point implementations of EMPC 
through mixed integer programming is given by~\citet{imperialrmpc}.
